---
title: "Hard Reset Analysis"
output:
  html_notebook: default
---

### Loading Packages
We load the required libraries.
```{r echo=T,eval=T,warning=FALSE, message=FALSE}
library("tidyverse")
library("lubridate")
```

<br><br>

### Loading Data

Loading the data into a tibble. In that case the csv generated used the tabulation separator. Adapt the delim parameter to your specific use case (coma, semicolon etc).

#### All devices experiencing hard resets, crashes issues
```{r echo=F,eval=T,warning=FALSE, message=FALSE}

df.devices.hardresets <- read_delim(file = "./data-raw/samples/sample_devices_hardsresets_20200310.csv",
                                delim = "\t")
head(df.devices.hardresets)
```
<br/><br/>

#### All devices available in the company
```{r echo=F,eval=T,warning=FALSE, message=FALSE}
df.all.devices <- read_delim(file = "./data-raw/samples/sample_all_devices_20200310.csv",
                     delim = "\t")
head(df.all.devices)
```
<br/><br/>

#### All devices errors, crashes and hard resets events for last 7 days
```{r echo=F,eval=T,warning=FALSE, message=FALSE}

df.events <- read_delim(file = "./data-raw/samples/sample_events_device_errors_20200310.csv",
                        delim = "\t")

head(df.events)
```
<br/><br/>

#### All devices CPU, Memory, IO warnings for last 7 days
```{r echo=F,eval=T,warning=FALSE, message=FALSE}

df.warnings.4 <- read_delim(file = "./data-raw/samples/sample_device_warnings_20200304.csv",
                           delim = "\t")
df.warnings.5 <- read_delim(file = "./data-raw/samples/sample_device_warnings_20200305.csv",
                           delim = "\t")
df.warnings.6 <- read_delim(file = "./data-raw/samples/sample_device_warnings_20200306.csv",
                           delim = "\t")
df.warnings.7 <- read_delim(file = "./data-raw/samples/sample_device_warnings_20200307.csv",
                           delim = "\t")
df.warnings.9 <- read_delim(file = "./data-raw/samples/sample_device_warnings_20200309.csv",
                           delim = "\t")

df.warnings <- bind_rows(df.warnings.4, df.warnings.5, df.warnings.6, df.warnings.7, df.warnings.9)

head(df.warnings)
```
<br/><br/>


#### All devices installations
```{r echo=F,eval=T,warning=FALSE, message=FALSE}

df.installations <- read.csv2(file = "./data-raw/samples/sample_installations_events_March_4_10.csv",
                           sep = ";", quote = "\"")

head(df.installations)
```

<br/><br/>

### Data cleaning and processing

We will not show the code here. We just create the dateframes needed for the analysis.

```{r echo=F,eval=T,warning=FALSE, message=FALSE}

# Number of devices per OS
df.all.os <- df.all.devices %>%
  group_by(`OS version and architecture`) %>%
  summarize(devices_per_os = n())

df.all.os %>%
  arrange(-devices_per_os)

# Number of devices por Build
df.all.builds <- df.all.devices %>%
  group_by(`OS build`) %>%
  summarize(devices_per_build = n())

# Number of devices per Entity
df.all.entity <- df.all.devices %>%
  group_by(Entity) %>%
  summarize(devices_per_entity = n())

# Dataframes used to draw number of Models per manufacturer
df.all.os <- df.all.devices %>%
  group_by(`OS version and architecture`) %>%
  summarize(devices_per_os = n())

# Dataframes used to draw number of Models per manufacturer
df.all.manufactur <- df.all.devices %>%
  group_by(`Device manufacturer`) %>%
  summarize(devices_per_manufacturer = n())

# Dataframes used to draw number of Models (Lenovo only)
df.all.levovo <- df.all.devices %>%
  filter(`Device manufacturer` == "Lenovo") %>%
  group_by(`Device product version`) %>%
  summarize(devices_model = n())

# Dataframes used to draw number of hardresets per Entity
df.hardreset.entity <- df.events %>%
  inner_join(df.all.devices, by = c("Device name" = "Name")) %>%
  filter(Type =="hard reset") %>%
  group_by(Entity) %>%
  summarize(number_hardresets = n())

# Dataframes used to draw the number of hard resets per OS
df.hardreset.os <- df.events %>%
  inner_join(df.all.devices, by = c("Device name" = "Name")) %>%
  filter(Type =="hard reset") %>%
  group_by(`OS version and architecture`) %>%
  summarize(number_hardresets = n())

# Dataframes with all installs/uninstalls used for timeseries graphs with operations and hard resets
df.operations <- df.installations %>%
    mutate(Time = dmy_hms(Time.of.installation),
         Day = day(Time),
         Hour = hour(Time)) %>%
  group_by(Day,Hour, Operation.type) %>%
  summarize(number_operations = n())
```

<br/><br/>

### Creating graphs

#### Number of hard resets per build, Windows 10 Enterprise 1809 (64 bits)
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
# All Manufacturers
df.events  %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>% 
  group_by(`OS version and architecture`, `OS build`) %>%
  summarize(number_crashes = n()) %>%
  inner_join(df.all.builds, by = c("OS build" = "OS build")) %>%
  filter(grepl("Windows 10 Enterprise 1809 (64 bits)",`OS version and architecture`, fixed = T)) %>%
  ggplot(mapping = aes(x = reorder(`OS build`, -devices_per_build))) +
  geom_bar(mapping = aes(y = devices_per_build), stat = "identity", fill = "#EEF3F7", colour = "#1046A8") +
  geom_line(mapping = aes(y = number_crashes*5), stat = "identity", colour = "red", group = 1) +
  geom_point(mapping = aes(y = number_crashes*5), stat = "identity", colour = "red", group = 1) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name = "Hard Resets")) +
  theme_linedraw() +
  labs(x ="", y = "Number of devices", title = "Number of Hard Resets for Windows 10 Enterprise 1809 (64 bits)")+
  theme(text = element_text(size = 15),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y.right = element_text(vjust = 0.5, color = "red"),
        axis.text.y.right = element_text(color = "red"),
        plot.title = element_text(hjust = 0.5))
```

<br/><br/>

#### Number of hard resets per build, Windows 10 Enterprise 1709 (64 bits)
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
# All Manufacturers
df.events  %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>% 
  group_by(`OS version and architecture`, `OS build`) %>%
  summarize(number_crashes = n()) %>%
  inner_join(df.all.builds, by = c("OS build" = "OS build")) %>%
  filter(grepl("Windows 10 Enterprise 1709 (64 bits)",`OS version and architecture`, fixed = TRUE)) %>%
  ggplot(mapping = aes(x = reorder(`OS build`, -devices_per_build))) +
  geom_bar(mapping = aes(y = devices_per_build), stat = "identity", fill = "#EEF3F7", colour = "#1046A8") +
  geom_line(mapping = aes(y = number_crashes*5), stat = "identity", colour = "red", group = 1) +
  geom_point(mapping = aes(y = number_crashes*5), stat = "identity", colour = "red", group = 1) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name = "Hard Resets")) +
  theme_linedraw() +
  labs(x ="", y = "Number of devices", title = "Number of Hard Resets for Windows 10 Enterprise 1709 (64 bits)")+
  theme(text = element_text(size = 15),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y.right = element_text(vjust = 0.5, color = "red"),
        axis.text.y.right = element_text(color = "red"),
        plot.title = element_text(hjust = 0.5))
```

<br/><br/>

#### Hard Resets by Device manufactureres

```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
# All Manufacturers
df.events  %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>% 
  group_by(`Device manufacturer`) %>%
  summarize(number_crashes = n()) %>%
  inner_join(df.all.manufactur, by = c("Device manufacturer" = "Device manufacturer")) %>%
  mutate(ratio_crashes_devices = number_crashes/devices_per_manufacturer*10) %>%
  ggplot(mapping = aes(x=`Device manufacturer`)) +
  geom_col(mapping = aes(y = devices_per_manufacturer), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black", alpha = 0.9) +
  geom_col(mapping = aes(y = number_crashes*5), fill = "#FF7461", width = .4, position = position_nudge(.2), colour = "Black", alpha = 0.9) +
  theme_linedraw() +
  labs(x ="",y = "Devices", title = "Hard Resets by manufactureres")+
  scale_y_continuous(sec.axis = sec_axis(~ . /5 ,name = "Hard resets")) +
  theme(
    axis.title.y.right = element_text(vjust = 0.5, color = "#FF7461"),
    axis.text.y.right = element_text(color = "#FF7461"),
    text = element_text(size = 18),
    plot.title = element_text(hjust = 0.5)
  )
```

<br/><br/>

#### Hard reset for Lenovo models

```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=15,fig.height=8}
#Lenovo Only
df.events  %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>% 
  filter(`Device manufacturer` == "Lenovo") %>%
  group_by(`Device manufacturer`, `Device product version`) %>%
  summarize(number_of_crashes= n()) %>%
  inner_join(df.all.levovo, by = c("Device product version" = "Device product version" )) %>%
  mutate(ratio_crashes_device_model = number_of_crashes/devices_model) %>%
  arrange(desc(ratio_crashes_device_model)) %>%
  ggplot(mapping = aes(x=`Device product version`)) +
  geom_col(mapping = aes(y = devices_model), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black", alpha = 0.9) +
  geom_col(mapping = aes(y = number_of_crashes*5), fill = "#FF7461", width = .4, position = position_nudge(.2), colour = "Black", alpha = 0.9) +
  theme_linedraw() +
  labs(x ="",y = "Devices", title = "Hard Resets for Lenovo Models")+
  scale_y_continuous(sec.axis = sec_axis(~ . /5 ,name = "Hard Resets")) +
  theme(
    axis.title.y.right = element_text(vjust = 0.5, color = "#FF7461"),
    axis.text.y.right = element_text(color = "#FF7461"),
    text = element_text(size = 18),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )
``` 



<br/><br/>

#### Hard reset classified by Error Code

```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.events %>%
  mutate(Issue_Time = dmy_hms(Time)) %>%
  mutate(Issue_Time = round_date(Issue_Time, unit = "day")) %>%
  group_by(Issue_Time, `Error code`) %>%
  summarize(count_n = n()) %>%
  filter(`count_n` > 1) %>%
  ggplot() +
  geom_bar(mapping = aes(x = Issue_Time, y = count_n, fill = `Error code`), stat = "identity", color = "black", alpha=0.7) +
  theme_minimal() +
  scale_fill_manual(values = c("#111F65", "#3194F7", "#1046A8", "#F9BA37", "#BA74D2", "#08B3AB", "#FF7461", "#B3BBC8", "#F7F9FB", "#63676E")) +
  labs(x= "",y = "Number of crashes", title = "Number of Hard Resets last 7 days grouped by Error Code") +
  theme(text = element_text(size = 18),
        plot.title = element_text(hjust = 0.5))
```


<br/><br/>

#### Evoluation of hard resets over time

```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.events %>%
  mutate(Time = dmy_hms(Time),
         Day = day(Time),
         Hour = hour(Time)) %>%
  group_by(Day,Hour) %>%
  summarize(count_n = n()) %>%
  filter(Day != 10) %>%
  ggplot() +
  geom_line(mapping = aes(x = Hour, y = count_n), color = "red") +
  geom_point(mapping = aes(x = Hour, y = count_n), color = "red") +
  facet_wrap(~Day) +
  theme_light() +
  labs(x = "",y = "Hard Resets", title = "Number of hard resets from 4th to 9th of March") +
  theme(strip.background = element_rect(
        color="black", fill="#EEF3F7", size=0.5, linetype="solid"),
        strip.text = element_text(color = "black"),
        plot.title = element_text(hjust = 0.5),
        text = element_text(size = 15))
```



<br/><br/>

#### Hard resets compared to Installs and Uninstalls

```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.events %>%
  mutate(Time = dmy_hms(Time),
         Day = day(Time),
         Hour = hour(Time)) %>%
  group_by(Day,Hour) %>%
  summarize(number_hard_resets = n()) %>%
  inner_join(df.operations, c("Day" = "Day", "Hour" = "Hour")) %>%
  filter(Day != 10) %>%
  ggplot() +
  geom_line(mapping = aes(x = Hour, y = number_hard_resets*10), color = "red", stat = "identity") +
  #geom_point(mapping = aes(x = Hour, y = number_hard_resets), color = "orange") +
  geom_freqpoly(mapping = aes(x = Hour, y = number_operations), stat = "identity", colour = "blue") +
  scale_y_continuous(sec.axis = sec_axis(~./10, name = "Hardresets")) +
  facet_wrap(~Day) +
  theme_light() +
  labs(x = "", y = "Installations and Uninstallations", title = "Hard resets and Operations") +
  theme(strip.background = element_rect(
        color="black", fill="#EEF3F7", size=0.5, linetype="solid"),
        axis.title.y.right = element_text(vjust = 0.5, color = "red"),
        axis.text.y.right = element_text(color = "red"),
        strip.text = element_text(color = "black"),
        plot.title = element_text(hjust = 0.5),
        text = element_text(size = 15))
```

<br/><br/>

#### Package type 
Let's focus on days 5, and see what operations are being performed between 7.30 AM and 10 AM

```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.installations %>%
  mutate(Time.of.installation = dmy_hms(Time.of.installation)) %>%
  filter(day(Time.of.installation) %in% c(5) & (hour(Time.of.installation) > 7.5 & hour(Time.of.installation) < 10)) %>%
  group_by(Package.name, Package.version, Package.type) %>%
  summarize(count_n = n()) %>%
  arrange(-count_n)
```

<br/><br/>

#### Operation type
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.events %>%
  mutate(Time = dmy_hms(Time),
         Day = day(Time),
         Hour = hour(Time)) %>%
  group_by(Day,Hour) %>%
  summarize(number_hard_resets = n()) %>%
  inner_join(df.operations, c("Day" = "Day", "Hour" = "Hour")) %>%
  filter(Day == 5) 
```


<br/><br/>

#### Number of logons over time
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.devices.hardresets %>%
  mutate(Logon_Time = dmy_hms(`Last logon time`),
         Logon_Day = day(Logon_Time),
         Logon_Hour = hour(Logon_Time)) %>%
  group_by(Logon_Day, Logon_Hour) %>%
  summarize(count_n = n()) %>%
  ungroup() %>%
  filter(Logon_Day %in% c(4,5,6,7,8,9)) %>%
  ggplot() +
  geom_line(mapping = aes(x = Logon_Hour, y = count_n), color = "blue",group = 1) +
  geom_point(mapping = aes(x = Logon_Hour, y = count_n), color = "orange",group = 1) +
  facet_wrap(~Logon_Day) +
  theme_light() +
  labs(x = "",y = "Number of Logons", title = "Number of logons from 4th to the 9th of March") +
  theme(strip.background = element_rect(
    color="black", fill="#3194F7", size=1, linetype="solid"),
    plot.title = element_text(hjust = 0.5),
    text = element_text(size = 15))
```




<br/><br/>



#### Number of hard reset by locations
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=16,fig.height=10}
df.warnings %>%
  inner_join(df.all.devices, by = c("Device name" = "Name")) %>%
  mutate(type = ifelse(grepl("cpu", .$`Event info`), "CPU", ifelse(grepl("memory", .$`Event info`),"Memory", "IO"))) %>%
  filter(type == "CPU") %>%
  group_by(Entity) %>%
  summarize(warning_counts = n()) %>%
  inner_join(df.all.entity, ., by = c("Entity" = "Entity")) %>%
  inner_join(df.hardreset.entity, by = c("Entity" = "Entity")) %>%
  mutate(ratio_crashes_devices = number_hardresets/devices_per_entity,
         ratio_warnings_devices = warning_counts/devices_per_entity) %>%
 ggplot(mapping = aes(x=`Entity`)) +
  geom_col(mapping = aes(y = devices_per_entity), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black", alpha = 0.9) +
  #geom_line(mapping = aes(y = warning_counts), stat = "identity", group =1, colour ="#F9BA37") +
  geom_col(mapping = aes(y = number_hardresets*7), fill = "#FF7461", width = .4, position = position_nudge(.2), colour = "Black", alpha = 0.9) +
  geom_label(aes(y = devices_per_entity + 400, label = paste("#Warnings\n",warning_counts)), colour = "red", size = 5) +
  theme_linedraw() +
  labs(x ="",y = "Number of Devices", title = "Hard Resets by Entity")+
  scale_y_continuous(sec.axis = sec_axis(~ . /7 ,name = "Number of Hardresets")) +
  theme(
    axis.title.y.right = element_text(vjust = 0.5, color = "#FF7461"),
    axis.text.y.right = element_text(color = "#FF7461"),
    text = element_text(size = 24),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  )
```


<br/><br/><br/>

#### Hard reset by OS
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=15,fig.height=8}
df.warnings %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>%
  mutate(type = ifelse(grepl("cpu", .$`Event info`), "CPU", ifelse(grepl("memory", .$`Event info`),"Memory", "IO"))) %>%
  filter(type == "CPU") %>%
  group_by(`OS version and architecture`) %>%
  summarize(warning_counts = n()) %>%
  inner_join(df.all.os, ., by = c("OS version and architecture" = "OS version and architecture")) %>%
  inner_join(df.hardreset.os, by = c("OS version and architecture" = "OS version and architecture")) %>%
  mutate(ratio_crashes_devices = number_hardresets/devices_per_os,
         ratio_warnings_devices = warning_counts/devices_per_os) %>%
  mutate(`OS version and architecture` = str_remove_all(`OS version and architecture`," \\(.*\\)")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Windows", "W")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Enterprise", "E")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Professional", "Pro")) %>%
  ggplot(mapping = aes(x=`OS version and architecture`)) +
  geom_col(mapping = aes(y = devices_per_os), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black", alpha = 0.9) +
  #geom_line(mapping = aes(y = warning_counts), stat = "identity", group =1, colour ="#F9BA37") +
  geom_col(mapping = aes(y = number_hardresets*7), fill = "#FF7461", width = .4, position = position_nudge(.2), colour = "Black", alpha = 0.9) +
  geom_label(aes(y = devices_per_os + 700, label = paste("#Warnings\n",warning_counts)), colour = "red", size = 5) +
  theme_linedraw() +
  labs(x ="",y = "Number of Devices", title = "Hard Resets by OS")+
  scale_y_continuous(sec.axis = sec_axis(~ . /7 ,name = "Number of Hardresets")) +
  theme(
    axis.title.y.right = element_text(vjust = 0.5, color = "#FF7461"),
    axis.text.y.right = element_text(color = "#FF7461"),
    text = element_text(size = 18),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  )
```


<br/><br/>

#### Crashes vs most recent Windows update
```{r echo=T,eval=T,warning=FALSE, message=FALSE, fig.width=15,fig.height=7}
df.devices.hardresets %>%
  mutate(`Last system update` = dmy_hms(`Last system update`)) %>%
  na.omit() %>%
  mutate(Last_update_year = year(`Last system update`),
         Last_update_month = month(`Last system update`),
         Last_update_month_year = paste(Last_update_year,Last_update_month, sep = "/")) %>%
  mutate(Last_update_month_year = ymd(Last_update_month_year, truncated = 1)) %>%
  mutate(`OS version and architecture` = str_remove_all(`OS version and architecture`," \\(.*\\)")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Windows", "W")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Enterprise", "E")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Professional", "Pro")) %>%
  group_by(Last_update_month_year, `OS version and architecture`) %>%
  summarize(number_devices_with_crashes = n()) %>%
  ggplot(aes( x= `Last_update_month_year`)) +
  geom_bar(aes(y = number_devices_with_crashes, fill = `OS version and architecture`), stat = "identity", position = "stack", color = "black", alpha = 0.8) +
  labs(x = "Last Windows update", title = "Number of devices with crashes last 7 days", fill = "OS") +
  theme_minimal() +
  scale_fill_manual(values = c("#111F65", "#3194F7", "#1046A8", "#F9BA37", "#BA74D2", "#08B3AB", "#FF7461")) +
  scale_x_date(date_breaks="2 month", date_labels="%Y %m") + 
  theme(text = element_text(size = 15),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(margin = margin(t = 20, b = 20)),
        axis.title.y = element_blank())
```





```{r echo=F,eval=F,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
# All Manufacturers
df.events  %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>% 
  group_by(`Device manufacturer`) %>%
  summarize(number_crashes = n()) %>%
  inner_join(df.all.manufactur, by = c("Device manufacturer" = "Device manufacturer")) %>%
  mutate(ratio_crashes_devices = number_crashes/devices_per_manufacturer*10) %>%
  ggplot(aes(x = reorder(`Device manufacturer`, -devices_per_manufacturer))) +
  geom_bar(mapping = aes(y = ratio_crashes_devices), stat = "identity", fill = "#111F65", color = "orange") +
  geom_text(aes(y = (ratio_crashes_devices + 0.1), label = paste("",devices_per_manufacturer))) +
  labs(x = "", y ="", title = "Ratio of Crashes per Number of Devices, by Manufacturer") +
  theme_minimal() +
  theme(text = element_text(size = 15),
        plot.title = element_text(hjust = 0.5))
ggsave("images/ratio_crashes_devices_by_manufacturer.png")
```

```{r echo=F,eval=F,warning=FALSE, message=FALSE, fig.width=15,fig.height=8}
#Lenovo Only
df.events  %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>% 
  filter(`Device manufacturer` == "Lenovo") %>%
  group_by(`Device manufacturer`, `Device product version`) %>%
  summarize(number_of_crashes= n()) %>%
  inner_join(df.all.levovo, by = c("Device product version" = "Device product version" )) %>%
  mutate(ratio_crashes_device_model = number_of_crashes/devices_model) %>%
  arrange(desc(ratio_crashes_device_model)) %>%
  ggplot(aes(x = reorder(`Device product version`, -devices_model))) +
  geom_bar(aes(y = ratio_crashes_device_model), stat = "identity", fill = "#111F65", color = "orange") +
  geom_text(aes(y = (ratio_crashes_device_model + 0.05), label = paste("",devices_model)))+
  labs(x = "", y ="",title = "Ratio of Crashes per Number of devices, by Lenovo Models")+
  theme_minimal() +
  theme(text = element_text(size = 15),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("images/ratio_crashes_devices_for_lenovo.png")
``` 


```{r echo=F,eval=F,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.warnings %>%
  inner_join(df.devices.hardresets, by = c("Device name" = "Name")) %>%
  mutate(type = ifelse(grepl("cpu", .$`Event info`), "CPU", ifelse(grepl("memory", .$`Event info`),"Memory", "IO"))) %>%
  filter(type == "CPU") %>%
  group_by(`OS version and architecture`) %>%
  summarize(warning_counts = n()) %>%
  inner_join(df.all.os, ., by = c("OS version and architecture" = "OS version and architecture")) %>%
  inner_join(df.hardreset.os, by = c("OS version and architecture" = "OS version and architecture")) %>%
  mutate(ratio_crashes_devices = number_hardresets/devices_per_os,
         ratio_warnings_devices = warning_counts/devices_per_os) %>%
  mutate(`OS version and architecture` = str_remove_all(`OS version and architecture`," \\(.*\\)")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Windows", "W")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Enterprise", "E")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Professional", "Pro")) %>%
  ggplot(aes(x = reorder(`OS version and architecture`, desc(devices_per_os)))) +
  geom_bar(mapping = aes(y = ratio_crashes_devices, colour = "Crashes by Devices"), fill="#EEF3F7", alpha = 0.7,
           stat = "identity") +
  geom_text(aes(y = (ratio_crashes_devices + 0.05), label = paste("",devices_per_os))) +
  geom_line(mapping = aes(y = ratio_warnings_devices/10), stat = "identity", group =1, colour ="#F9BA37") +
  geom_point(mapping = aes(y = ratio_warnings_devices/10, colour = "Warnings by Devices"), stat = "identity", group =1) +
  labs(x = "", y = "Crashes", colour = "", title = "Ratio of crashes/warnings per Number of devices per OS") +
  scale_y_continuous(sec.axis = sec_axis(~.*30, name = "Warnings")) +
  theme_light() +
  scale_colour_manual(values = c("#1046A8", "#F9BA37")) +
  theme(text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))
ggsave("images/ratio_crashes_warnings_by_devices_OS.png")
```



```{r echo=F,eval=F,warning=FALSE, message=FALSE, fig.width=13,fig.height=8}
df.warnings %>%
  inner_join(df.all.devices, by = c("Device name" = "Name")) %>%
  mutate(type = ifelse(grepl("cpu", .$`Event info`), "CPU", ifelse(grepl("memory", .$`Event info`),"Memory", "IO"))) %>%
  filter(type == "CPU") %>%
  group_by(Entity) %>%
  summarize(warning_counts = n()) %>%
  inner_join(df.all.entity, ., by = c("Entity" = "Entity")) %>%
  inner_join(df.hardreset.entity, by = c("Entity" = "Entity")) %>%
  mutate(ratio_crashes_devices = number_hardresets/devices_per_entity,
         ratio_warnings_devices = warning_counts/devices_per_entity) %>%
  ggplot(aes(x = reorder(Entity, desc(devices_per_entity)))) +
  geom_bar(mapping = aes(y = ratio_crashes_devices, colour = "Crashes by Devices"), stat = "identity", fill="#EEF3F7") +
  geom_text(aes(y = (ratio_crashes_devices + 0.05), label = paste("",devices_per_entity))) +
  geom_line(mapping = aes(y = ratio_warnings_devices/30), stat = "identity", group =1, colour ="#F9BA37") +
  geom_point(mapping = aes(y = ratio_warnings_devices/30, colour = "Warnings by Devices"), stat = "identity", group =1) +
  labs(x = "", y = "Crashes", colour = "", title = "Ratio of crashes/warnings per Number of devices per Entity") +
  scale_y_continuous(sec.axis = sec_axis(~.*30, name = "Warnings")) +
  theme_light() +
  scale_colour_manual(values = c("#1046A8", "#F9BA37")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))
ggsave("images/ratio_crashes_warnings_by_devices_entity.png")
```